---
title: "Using the lab4 package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the lab4 package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This package fits linear regression models using QR decomposition.
It uses an S3 class called linreg.

We use the iris dataset to predict petal length from flower species.

```{r}
library(lab4)

model <- linreg(Petal.Length ~ Species, data = iris)
```

## Print the model

The print method displays the model call and its coefficients.

```{r}
print(model)
```

## Coefficients

The intercept is the estimated mean petal length for setosa.
The other coefficients describe differences from setosa.

```{r}
coef(model)
```

## Residuals

A residual is the observed value minus the fitted value.
Here are the first six residuals.

```{r}
head(resid(model))
```

## Fitted values

The pred method returns predictions for the observations used
to fit the model.

```{r}
head(pred(model))
```

## Model summary

The summary displays coefficient estimates, standard errors,
t-values and p-values. It also displays the residual standard
error and residual degrees of freedom.

```{r}
summary(model)
```

## Diagnostic plots

The first plot shows residuals against fitted values.
Patterns may suggest that the model does not describe the data well.

The Scale-Location plot helps assess whether the spread of
errors changes across fitted values.

```{r, fig.width=6, fig.height=4}
plot(model)
```

## Multiple predictors

We can also predict petal length using sepal length and sepal width.

```{r}
model2 <- linreg(
  Petal.Length ~ Sepal.Length + Sepal.Width,
  data = iris
)

summary(model2)
```
